---
title: "Assignment 1"
---

# Part A

-   Unavailable for now

# Part B

-   *I got help a [website](https://rnotlari.netlify.app/post/2020-10-17-hangi-apply-fonksiyonunu-kullan%C4%B1r%C4%B1z/) for using "sapply()" and "lapply()". I also got a little help from gpt on the "kable()" function.*
-   If the package does not open, install the package by (tool\>install package) and try again.

```{r}
library(knitr)
library(dslabs)  
data("polls_us_election_2016")
```

-   The first 10 rows of the data set

```{r}
kable(head(polls_us_election_2016, 10))
```

-   Total number of NA values in the entire data set

```{r}
total_of_numbers_NA <- sum(is.na(polls_us_election_2016))
total_of_numbers_NA
```

-   For numeric columns, replace NA values with my birth year

```{r}
numerc_columns <- sapply(polls_us_election_2016, FUN=is.numeric) 
polls_us_election_2016[numerc_columns] <- lapply(polls_us_election_2016[numerc_columns], function(x) {
  my_birthyear <- 2003
  ifelse(is.na(x), my_birthyear, x)
  })
```

-   Replace NA values with my first name for character columns.

```{r}
character_col <- sapply(polls_us_election_2016, FUN=is.character)
polls_us_election_2016[character_col] <- lapply(polls_us_election_2016[character_col], function(y) {  #sapply() da lapply() da denedim
  my_name <- "Ahmet"
  ifelse(is.na(y), my_name, y)
  })
```

-   Replace NA values with my first name for factor columns.

```{r}
factor_col <- sapply(polls_us_election_2016, FUN=is.factor)
polls_us_election_2016[factor_col] <- lapply(polls_us_election_2016[factor_col], function(z) {  #sapply() da lapply() da denedim
  my_name <- "Ahmet"
  z <- as.character(z) #got help from gpt on this line
  ifelse(is.na(z), my_name, z)
  })
```

-   The modified data set is stored as a new object.

```{r}
new_object <- polls_us_election_2016
```

-   The first 10 rows of the new data frame and the total number of NAs remaining in the new data frame.

```{r}
kable(head(new_object, 10))
```

-   The total number of NAsremaining in the new data frame.

```{r}
total_numer_of_NAs_remaining <- sum(is.na(new_object))
total_numer_of_NAs_remaining
```
